A systematic search for transiting planets using \KT

### 2015-02-06 ms.tex
Working on intro

The \kepler\ Mission (cite something) has been incredibly succesful at
finding periodic transits (eclipses) in the light curves (time-series
photometry) of stars.
Many of its most important discoveries are long-period planets that
make transits with tiny amplitudes and short durations relative to the
planet's orbital period.
The Mission has demonstrated that it is possible to routinely measure
signals in stellar light curves at the part-in-$10^5$ level, at least
for quiet and apparently bright stars.

At this level of precision, many effects come in to play in a stellar
light curve.
Even in a space observatory like the \kepler\ Satellite, there are
hardware and optics variations that affect simple photometric
measurements at a level greater than part-in-$10^5$.
One of the most serious of these is spacecraft pointing:
If the detector flat-field is not known \emph{exquisitely}, then the
tiny changes to the relative illumination of pixels caused by a star's
motion in the focal plane (or caused by motion of the focal-plane
boresight or orientation relative to the celestial sphere) will lead
to changes in the measured or inferred brightness of the star.
That is, good photometry relies on either a near-perfect flat-field
and pointing model, or else data-analysis techniques that are
insensitive to such variations.
In this \paper\ we present an example of the latter---a
data-analysis technique for exoplanet search and characterization that
is insensitive to spacecraft-induced (or, in general,
hardware-induced) trends in the light curves.

The \KT\ Mission (cite something-Howell 14) is a follow-on to the primary
\kepler\ Mission.
The primary mission came to an end with the failure of a critical
reaction wheel, rendering the spacecraft less able to maintain precise
pointing.
Because of the degraded spacecraft orientation systems, the new
\KT\ data will in general exhibit far greater pointing
variations---and far greater pointing-induced variations in
photometry---than the original \kepler\ data.
This makes good data-analysis techniques all the more valuable.

>>>>

The \kepler\ Mission (cite something) has been incredibly succesful at
finding periodic transits (eclipses) in the light curves (time-series
photometry) of stars (cite something).
The Mission has demonstrated that it is possible to routinely measure
signals in stellar light curves at the part-in-$10^5$ level.
Results from the primary mission include the detection of planet
transits with depths as small as (XX) parts per million (cite Barclay).

The noise floor for \kepler\ data is often quoted as 15 parts per million per
six hours of observations (cite someone- Gilliland 11?). 
Although they generally do not influence the ability to search for transiting
planets, larger systematic (noise shits) exist on different timescales. 
One of the most serious of these is spacecraft pointing:
If the detector flat-field is not known \emph{exquisitely}, then
tiny changes to the relative illumination of pixels caused by a star's
motion in the focal plane (or caused by motion of the focal-plane
boresight or orientation relative to the celestial sphere) will lead
to changes in the measured or inferred brightness of the star.

The pointing of \kepler\ was stable at the (LEVEL) level (citation) throughout
the primary mission. 
This primary mission came to an end with the failure of a critical
reaction wheel, rendering the spacecraft less able to maintain precise
pointing.
The \KT\ Mission (cite something-Howell 14) is a follow-on to the primary
\kepler\ Mission, observing approximately a dozen fields near the ecliptic
plane, each for 75 days at a time.
Because of the degraded spacecraft orientation systems, the new
\KT\ data will in general exhibit far greater pointing
variations---and far greater pointing-induced variations in
photometry---than the original \kepler\ data.
This makes good data-analysis techniques extremely valuable.

Good photometry relies on either a near-perfect flat-field
and pointing model or data-analysis techniques that are
insensitive to such variations.
The flat-field for \kepler\ was measured on the ground before the launch of 
the spacecraft, but (blah blah it sucks for describing the FF now).
Inference of the flat field is challenging because of the nature of the
spacecraft's observations: point sources are observed with relatively limited
spacecraft motion, and only a few percent of the data are actually stored and
downloaded to Earth.
Therefore, much of the effort in \KT\

In this \paper\ we present an example of the latter---a
data-analysis technique for exoplanet search and characterization that
is insensitive to spacecraft-induced (or, in general,
hardware-induced) trends in the light curves.
